### 2023-01-13 about/vita.tex
Update vita

@@

\starleftright{\bf Infantryman}{\bf August 2015 -- August 2017}
\leftright{\sl Singapore Armed Forces}{\sl Singapore}
\smallskip
Held appointment of machine-gun team commander in the 3rd Battalion, Singapore Infantry Regiment.
Led a six-person team consisting of a medic, signaller, sensor, and two-machine gunners within a rifle platoon.
\medbreak

>>>>

\starleftright{\bf After school care supervisor}{\bf January 2023 -- present}
\leftright{\bf Suzuki Charter School}{\sl Edmonton, AB, Canada}
\smallskip
Supervise and facilitate activities (e.g., arts and crafts, dodgeball, drawing/colouring) for children
in grades 1 through 6.
\medbreak

\starleftright{\bf Software developer}{\bf January 2023 -- present}
\leftright{\bf Levven}{\sl Edmonton, AB, Canada}
\smallskip
Develop firmware for the manufacture and function of in-home IoT gateways, smart switches,
and related electronic products. Code primarily in \CEE\ and Python.
\medbreak

@@

\starleftright{\bf Infantryman}{\bf August 2015 -- August 2017}
\leftright{\sl Singapore Armed Forces}{\sl Singapore}
\smallskip
Held appointment of machine-gun team commander in the 3rd Battalion, Singapore Infantry Regiment.
Led a six-person team consisting of a medic, signaller, sensor, and two-machine gunners within a rifle platoon.
Most recent reserve training: December 2022.
\medbreak
